Outputs from time slice analyses

### 2017-12-06 analyses/03-statistical-analyses.Rmd
Remove bears

out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))
#out1 <- readRDS(file = paste0("../outputs/epoch.", slug, ".Rda"))

@@

```{r}
slug <- "Beck2014" ; extinction <- 66.0
# slug <- "Brusatte2014"; extinction <- 66.0
# slug <- "Bapst2016"; extinction <- 66.0
# slug <- "bears"; extinction <- NA
# slug <- "Wright2017"; extinction <- 443.0
```

@@

```{r}
slug <- "Beck2014"
#slug <- "Brusatte2014"
#slug <- "Bapst2016"
#slug <- "bears"
#slug <- "Wright2017"
```

>>>>

#out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))
out1 <- readRDS(file = paste0("../outputs/epoch.", slug, ".Rda"))

@@

```{r}
slug <- "Beck2014" ; extinction <- 66.0
# slug <- "Brusatte2014"; extinction <- 66.0
# slug <- "Bapst2016"; extinction <- 66.0
# slug <- "Wright2017"; extinction <- 443.0
```

@@

```{r}
slug <- "Beck2014"
#slug <- "Brusatte2014"
#slug <- "Bapst2016"
#slug <- "Wright2017"
```
